A Fredholm operator approach to eigenvalue problems in elasticity and planar Stokes flow

### 2019-01-23 doc/draft-01-stokes/01intro.tex
adding stokes paper stuff

\begin{remark}
  When $k = i\alpha$, the differential equation
  \cref{eq:buck1} is known as the modified biharmonic
  equation. As there appears to be no preferred
  name for the equation with real-valued $k$,
  we will refer to \cref{eq:buck1} as the
  Helmholtz-biharmonic equation.
\end{remark}

>>>>

\begin{remark}
  When $k = i\alpha$, the differential equation
  \cref{eq:buck1} is known as the modified biharmonic
  equation. As there appears to be no preferred
  name for the equation with real-valued $k$,
  we will refer to \cref{eq:buck1} as the
  oscillatory biharmonic equation.
\end{remark}
